Results

### 2024-04-12 results.RmD
deleting large files

---
title: "Who needs privacy? Exploring the relations between need for privacy and personality"
subtitle: "Analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
---

@@

knitr::opts_chunk$set(
  warning=F, 
  echo=F, 
  error=F, 
  message=F, 
  cache = T, 
  tidy=T, 
  dev = 'pdf', 
  cache.extra = knitr::rand_seed
  )

@@

# Set-Up
## Packages

```{r r-setup, include=T, echo=T, results='hide'}
# install packages
# devtools::install_github("https://github.com/tdienlin/td")

library(confintr)
library(corrplot)
library(devtools)
library(easystats)
library(GGally)
library(ggplot2)
library(haven)
library(kableExtra)
library(knitr)
library(lavaan)
library(magrittr)
library(mice)
library(MVN)
library(naniar)
library(PerFit)
library(psych)
library(quanteda.textstats)
library(pwr)
library(semPlot)
library(sjlabelled)
library(simsem)
library(semTools)
library(tidyverse)
library(td)

load("data/workspace_1.RData")
source("custom_functions.R")
```

```{r data-wrangling}
# d <- read_spss("data/Need+for+Privacy_February+27%2C+2023_13.45.sav")
d_raw <- sjlabelled::read_spss(
  "data/Need+for+Privacy_February+6%2C+2024_15.56.sav",
  convert.factors = FALSE
  )
```

### Data-Wrangling

```{r data-inverting}
vars_invert <- c(
  "HEX_HOH_SIN_01", "HEX_HOH_SIN_03",
  "HEX_HOH_FAI_01", "HEX_HOH_FAI_02", "HEX_HOH_FAI_04",
  "HEX_HOH_GRE_02", "HEX_HOH_GRE_03", "HEX_HOH_GRE_04",
  "HEX_HOH_MOD_03", "HEX_HOH_MOD_04",
  "HEX_EMO_FEA_02", "HEX_EMO_FEA_04",
  "HEX_EMO_ANX_02", "HEX_EMO_ANX_03",
  "HEX_EMO_DEP_02", "HEX_EMO_DEP_04",
  "HEX_EMO_SEN_04",
  "HEX_EXT_SSE_03", "HEX_EXT_SSE_04",
  "HEX_EXT_BOL_01", "HEX_EXT_BOL_04",
  "HEX_EXT_SOC_01",
  "HEX_EXT_LIV_03", "HEX_EXT_LIV_04",
  "HEX_AGR_FOR_03", "HEX_AGR_FOR_04",
  "HEX_AGR_GEN_01",
  "HEX_AGR_FLX_01", "HEX_AGR_FLX_03", "HEX_AGR_FLX_04",
  "HEX_AGR_PAT_01", "HEX_AGR_PAT_04",
  "HEX_CNS_ORG_03", "HEX_CNS_ORG_04",
  "HEX_CNS_DIL_03", "HEX_CNS_DIL_04",
  "HEX_CNS_PER_02",
  "HEX_CNS_PRU_01", "HEX_CNS_PRU_02", "HEX_CNS_PRU_04",
  "HEX_OPN_AES_01", "HEX_OPN_AES_02",
  "HEX_OPN_INQ_03", "HEX_OPN_INQ_04",
  "HEX_OPN_CRE_01", "HEX_OPN_CRE_04",
  "HEX_OPN_UNC_01", "HEX_OPN_UNC_04",
  "HEX_ALT_03", "HEX_ALT_04",
  "NFP_COM_02"
)

d <-
  d_raw %>% 
  rename(
    COL = COL_,
    REL = REL_
    ) %>%
  mutate(
    across(all_of(vars_invert),
    ~ 8 - .x
         ),
    male = case_match(
      GEN,
      c(2, 3) ~ 0,
      1 ~ 1),
    age = case_match(
      AGE,
      1 ~ 1,
      2 ~ 2,
      3 ~ 3,
      4 ~ 4,
      5 ~ 7,
      6 ~ 5,
      7 ~ 6),
    white = case_match(
      ETH,
      2 ~ 0,
      1 ~ 1),
    relation = case_match(
      REL,
      2 ~ 1,
      1 ~ 0),
    college = case_match(
      COL,
      2 ~ 1,
      1 ~ 0),
    conserv = CON,
    income = INC
  ) 
```

### Labels

```{r data-labels}
# define vars and labels
vars_ses <- c("age", "male", "white", "relation", "college", "income", "conserv")
vars_ses_txt <- c("Age", "Male", "White", "Relationship", "College", "Income", "Conservatism")

vars_pers_fac <- c("HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD",
                   "HEX_ALT",
                   "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN", 
                   "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV", 
                   "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT", 
                   "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU", 
                   "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC")
vars_pers_fac_txt <- c("Sincerity", "Fairness", "Greed avoidance", "Modesty", 
                       "Altruism",
                       "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
                       "Social self-esteem", "Social boldness", "Sociability", "Liveliness",
                       "Forgiveness", "Gentleness", "Flexibility", "Patience", 
                       "Organization", "Diligence", "Perfectionism", "Prudence", 
                       "Aesthetic\nappreciation", "Inquisitiveness", "Creativeness", "Unconventionality")

vars_pers_hoh <- 
  c("HEX_HOH", "HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD", "HEX_ALT")
vars_pers_emo <- 
  c("HEX_EMO", "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN")
vars_pers_ext <- 
  c("HEX_EXT", "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV")
vars_pers_agr <- 
  c("HEX_AGR", "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT")
vars_pers_cns <- 
  c("HEX_CNS", "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU")
vars_pers_opn <- 
  c("HEX_OPN", "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC")

vars_pers_all <- 
  c(
    vars_pers_hoh, 
    vars_pers_emo, 
    vars_pers_ext, 
    vars_pers_agr, 
    vars_pers_cns,
    vars_pers_opn
    )

vars_pers_all_txt <- 
  c("Honesty humility", 
      "Sincerity", "Fairness", "Greed avoidance", "Modesty", "Altruism",
    "Emotionality", 
      "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
    "Extraversion",
      "Social self-esteem", "Social boldness", "Sociability", "Liveliness",
    "Agreeableness",
      "Forgiveness", "Gentleness", "Flexibility", "Patience",
    "Conscientiousness",
      "Organization", "Diligence", "Perfectionism", "Prudence", 
    "Openness",
      "Aesthetic\nappreciation", "Inquisitiveness", "Creativeness", "Unconventionality"
    )

vars_pred_all_txt <- 
  c(
    vars_pers_all_txt,
    vars_ses_txt
    )

vars_pers_dim <- c("HEX_HOH", "HEX_EMO", "HEX_EXT", "HEX_AGR", "HEX_CNS", "HEX_OPN")
vars_pers_dim_txt <- c("Honesty humility", "Emotionality", "Extraversion", 
                       "Agreeableness", "Conscientiousness", "Openness")

vars_pri <- c("NFP_PSY", "NFP_SOC", "NFP_PHY", 
              "NFP_GOV", "NFP_COM", 
              "NFP_INF", "NFP_ANO", "NFP_GEN")
vars_pri_txt <- c("Psychological", "Social", "Physical", 
                  "Government", "Companies", 
                  "Informational", "Anonymity", "General")
vars_pri_txt_brk <- c("Psycho-\nlogical", "Social", "Physical", 
                  "Govern-\nment", "Companies", 
                  "Infor-\nmational", "Anony-\nmity", "General")
vars_pri_txt_abr <- c("Psych.", "Social", "Phys.", 
                  "Gov.", "Comp.", 
                  "Inform.", "Anonym.", "General")

vars_pers_pri <- c(vars_pers_fac, vars_pri)
```

## Means

```{r}
# Person means per facet

d %<>%
  mutate(
    HEX_HOH_M = rowMeans(select(., starts_with("HEX_HOH"))),
    HEX_EMO_M = rowMeans(select(., starts_with("HEX_EMO"))),
    HEX_EXT_M = rowMeans(select(., starts_with("HEX_EXT"))),
    HEX_AGR_M = rowMeans(select(., starts_with("HEX_AGR"))),
    HEX_CNS_M = rowMeans(select(., starts_with("HEX_CNS"))),
    HEX_OPN_M = rowMeans(select(., starts_with("HEX_OPN"))),
    HEX_ALT_M = rowMeans(select(., starts_with("HEX_ALT_0"))),
    HEX_AGR_FLX_M = rowMeans(select(., starts_with("HEX_AGR_FLX_0"))),
    HEX_AGR_FOR_M = rowMeans(select(., starts_with("HEX_AGR_FOR_0"))),
    HEX_AGR_GEN_M = rowMeans(select(., starts_with("HEX_AGR_GEN_0"))),
    HEX_AGR_PAT_M = rowMeans(select(., starts_with("HEX_AGR_PAT_0"))),
    HEX_CNS_DIL_M = rowMeans(select(., starts_with("HEX_CNS_DIL_0"))),
    HEX_CNS_ORG_M = rowMeans(select(., starts_with("HEX_CNS_ORG_0"))),
    HEX_CNS_PER_M = rowMeans(select(., starts_with("HEX_CNS_PER_0"))),
    HEX_CNS_PRU_M = rowMeans(select(., starts_with("HEX_CNS_PRU_0"))),
    HEX_EMO_ANX_M = rowMeans(select(., starts_with("HEX_EMO_ANX_0"))),
    HEX_EMO_DEP_M = rowMeans(select(., starts_with("HEX_EMO_DEP_0"))),
    HEX_EMO_FEA_M = rowMeans(select(., starts_with("HEX_EMO_FEA_0"))),
    HEX_EMO_SEN_M = rowMeans(select(., starts_with("HEX_EMO_SEN_0"))),
    HEX_EXT_BOL_M = rowMeans(select(., starts_with("HEX_EXT_BOL_0"))),
    HEX_EXT_LIV_M = rowMeans(select(., starts_with("HEX_EXT_LIV_0"))),
    HEX_EXT_SOC_M = rowMeans(select(., starts_with("HEX_EXT_SOC_0"))),
    HEX_EXT_SSE_M = rowMeans(select(., starts_with("HEX_EXT_SSE_0"))),
    HEX_HOH_FAI_M = rowMeans(select(., starts_with("HEX_HOH_FAI_0"))),
    HEX_HOH_GRE_M = rowMeans(select(., starts_with("HEX_HOH_GRE_0"))),
    HEX_HOH_MOD_M = rowMeans(select(., starts_with("HEX_HOH_MOD_0"))),
    HEX_HOH_SIN_M = rowMeans(select(., starts_with("HEX_HOH_SIN_0"))),
    HEX_OPN_AES_M = rowMeans(select(., starts_with("HEX_OPN_AES_0"))),
    HEX_OPN_CRE_M = rowMeans(select(., starts_with("HEX_OPN_CRE_0"))),
    HEX_OPN_INQ_M = rowMeans(select(., starts_with("HEX_OPN_INQ_0"))),
    HEX_OPN_UNC_M = rowMeans(select(., starts_with("HEX_OPN_UNC_0"))),
    NFP_ANO_M = rowMeans(select(., starts_with("NFP_ANO_0"))),
    NFP_COM_M = rowMeans(select(., starts_with("NFP_COM_0"))),
    NFP_GEN_M = rowMeans(select(., starts_with("NFP_GEN_0"))),
    NFP_GOV_M = rowMeans(select(., starts_with("NFP_GOV_0"))),
    NFP_INF_M = rowMeans(select(., starts_with("NFP_INF_0"))),
    NFP_PHY_M = rowMeans(select(., starts_with("NFP_PHY_0"))),
    NFP_PSY_M = rowMeans(select(., starts_with("NFP_PSY_0"))),
    NFP_SOC_M = rowMeans(select(., starts_with("NFP_SOC_0")))
  )

# item means
c_m <- 
  c(
    HEX_ALT_m     = mean(d$HEX_ALT_M, na.rm = T),
    HEX_AGR_FLX_m = mean(d$HEX_AGR_FLX_M, na.rm = T),
    HEX_AGR_FOR_m = mean(d$HEX_AGR_FOR_M, na.rm = T),
    HEX_AGR_GEN_m = mean(d$HEX_AGR_GEN_M, na.rm = T),
    HEX_AGR_PAT_m = mean(d$HEX_AGR_PAT_M, na.rm = T),
    HEX_CNS_DIL_m = mean(d$HEX_CNS_DIL_M, na.rm = T),
    HEX_CNS_ORG_m = mean(d$HEX_CNS_ORG_M, na.rm = T),
    HEX_CNS_PER_m = mean(d$HEX_CNS_PER_M, na.rm = T),
    HEX_CNS_PRU_m = mean(d$HEX_CNS_PRU_M, na.rm = T),
    HEX_EMO_ANX_m = mean(d$HEX_EMO_ANX_M, na.rm = T),
    HEX_EMO_DEP_m = mean(d$HEX_EMO_DEP_M, na.rm = T),
    HEX_EMO_FEA_m = mean(d$HEX_EMO_FEA_M, na.rm = T),
    HEX_EMO_SEN_m = mean(d$HEX_EMO_SEN_M, na.rm = T),
    HEX_EXT_BOL_m = mean(d$HEX_EXT_BOL_M, na.rm = T),
    HEX_EXT_LIV_m = mean(d$HEX_EXT_LIV_M, na.rm = T),
    HEX_EXT_SOC_m = mean(d$HEX_EXT_SOC_M, na.rm = T),
    HEX_EXT_SSE_m = mean(d$HEX_EXT_SSE_M, na.rm = T),
    HEX_HOH_FAI_m = mean(d$HEX_HOH_FAI_M, na.rm = T),
    HEX_HOH_GRE_m = mean(d$HEX_HOH_GRE_M, na.rm = T),
    HEX_HOH_MOD_m = mean(d$HEX_HOH_MOD_M, na.rm = T),
    HEX_HOH_SIN_m = mean(d$HEX_HOH_SIN_M, na.rm = T),
    HEX_OPN_AES_m = mean(d$HEX_OPN_AES_M, na.rm = T),
    HEX_OPN_CRE_m = mean(d$HEX_OPN_CRE_M, na.rm = T),
    HEX_OPN_INQ_m = mean(d$HEX_OPN_INQ_M, na.rm = T),
    HEX_OPN_UNC_m = mean(d$HEX_OPN_UNC_M, na.rm = T),
    NFP_ANO_m     = mean(d$NFP_ANO_M, na.rm = T),
    NFP_COM_m     = mean(d$NFP_COM_M, na.rm = T),
    NFP_GEN_m     = mean(d$NFP_GEN_M, na.rm = T),
    NFP_GOV_m     = mean(d$NFP_GOV_M, na.rm = T),
    NFP_INF_m     = mean(d$NFP_INF_M, na.rm = T),
    NFP_PHY_m     = mean(d$NFP_PHY_M, na.rm = T),
    NFP_PSY_m     = mean(d$NFP_PSY_M, na.rm = T),
    NFP_SOC_m     = mean(d$NFP_SOC_M, na.rm = T),
    HEX_HOH_m     = mean(d$HEX_HOH_M, na.rm = T),
    HEX_EMO_m     = mean(d$HEX_EMO_M, na.rm = T),
    HEX_EXT_m     = mean(d$HEX_EXT_M, na.rm = T),
    HEX_AGR_m     = mean(d$HEX_AGR_M, na.rm = T),
    HEX_CNS_m     = mean(d$HEX_CNS_M, na.rm = T),
    HEX_OPN_m     = mean(d$HEX_OPN_M, na.rm = T)
  )

# item standard deviation
c_sd <- 
  c(
    HEX_ALT_sd     = sd(d$HEX_ALT_M, na.rm = T),
    HEX_AGR_FLX_sd = sd(d$HEX_AGR_FLX_M, na.rm = T),
    HEX_AGR_FOR_sd = sd(d$HEX_AGR_FOR_M, na.rm = T),
    HEX_AGR_GEN_sd = sd(d$HEX_AGR_GEN_M, na.rm = T),
    HEX_AGR_PAT_sd = sd(d$HEX_AGR_PAT_M, na.rm = T),
    HEX_CNS_DIL_sd = sd(d$HEX_CNS_DIL_M, na.rm = T),
    HEX_CNS_ORG_sd = sd(d$HEX_CNS_ORG_M, na.rm = T),
    HEX_CNS_PER_sd = sd(d$HEX_CNS_PER_M, na.rm = T),
    HEX_CNS_PRU_sd = sd(d$HEX_CNS_PRU_M, na.rm = T),
    HEX_EMO_ANX_sd = sd(d$HEX_EMO_ANX_M, na.rm = T),
    HEX_EMO_DEP_sd = sd(d$HEX_EMO_DEP_M, na.rm = T),
    HEX_EMO_FEA_sd = sd(d$HEX_EMO_FEA_M, na.rm = T),
    HEX_EMO_SEN_sd = sd(d$HEX_EMO_SEN_M, na.rm = T),
    HEX_EXT_BOL_sd = sd(d$HEX_EXT_BOL_M, na.rm = T),
    HEX_EXT_LIV_sd = sd(d$HEX_EXT_LIV_M, na.rm = T),
    HEX_EXT_SOC_sd = sd(d$HEX_EXT_SOC_M, na.rm = T),
    HEX_EXT_SSE_sd = sd(d$HEX_EXT_SSE_M, na.rm = T),
    HEX_HOH_FAI_sd = sd(d$HEX_HOH_FAI_M, na.rm = T),
    HEX_HOH_GRE_sd = sd(d$HEX_HOH_GRE_M, na.rm = T),
    HEX_HOH_MOD_sd = sd(d$HEX_HOH_MOD_M, na.rm = T),
    HEX_HOH_SIN_sd = sd(d$HEX_HOH_SIN_M, na.rm = T),
    HEX_OPN_AES_sd = sd(d$HEX_OPN_AES_M, na.rm = T),
    HEX_OPN_CRE_sd = sd(d$HEX_OPN_CRE_M, na.rm = T),
    HEX_OPN_INQ_sd = sd(d$HEX_OPN_INQ_M, na.rm = T),
    HEX_OPN_UNC_sd = sd(d$HEX_OPN_UNC_M, na.rm = T),
    NFP_ANO_sd     = sd(d$NFP_ANO_M, na.rm = T),
    NFP_COM_sd     = sd(d$NFP_COM_M, na.rm = T),
    NFP_GEN_sd     = sd(d$NFP_GEN_M, na.rm = T),
    NFP_GOV_sd     = sd(d$NFP_GOV_M, na.rm = T),
    NFP_INF_sd     = sd(d$NFP_INF_M, na.rm = T),
    NFP_PHY_sd     = sd(d$NFP_PHY_M, na.rm = T),
    NFP_PSY_sd     = sd(d$NFP_PSY_M, na.rm = T),
    NFP_SOC_sd     = sd(d$NFP_SOC_M, na.rm = T),
    HEX_HOH_sd     = sd(d$HEX_HOH_M, na.rm = T),
    HEX_EMO_sd     = sd(d$HEX_EMO_M, na.rm = T),
    HEX_EXT_sd     = sd(d$HEX_EXT_M, na.rm = T),
    HEX_AGR_sd     = sd(d$HEX_AGR_M, na.rm = T),
    HEX_CNS_sd     = sd(d$HEX_CNS_M, na.rm = T),
    HEX_OPN_sd     = sd(d$HEX_OPN_M, na.rm = T)
  )
```

# Missing data

First filter those who didn't finish the questionnaire.

```{r}
d %<>%
  filter(
    Progress == 100
  )

n_finished <- nrow(d)
```

Let's first inspect missing data.

How many missing do we have?

```{r}
n_miss(d)
prop_miss(d)
```

Only 23 cells are missing -- which is very little. To be precise, 0.00006 percent only.

Which variables are affected?

```{r}
miss_var_summary(d) %>% 
  head(19)
```

Missing answers vary randomly across variables.

How about participants?

```{r}
miss_case_summary(d)
```

Only six participants with missing data, and even then, not much. We hence decided to keep everyone.

# Quality checks

We preregistered to remove participants faster than 3 standard deviations than the median response time.

```{r cache=F}
# Median response time
time_med <- median(d$Duration__in_seconds_)

# Average response time
time_m <- mean(d$Duration__in_seconds_) / 60

# Standard deviation
time_sd <- sd(d$Duration__in_seconds_)

# filter speeders
time_crit_init <- time_med - (3 * time_sd) # minimum time on survey
```

However, this made little sense. The median response time was `r time_med` and the standard deviation `r time_sd`. Hence, three SDs below median was `r time_crit_init`, hence not informative.

Instead, we decided to remove respondents who took less than five minutes answering the questionnaire, which we considered unreasonably fast.

```{r cache=F}
time_crit <- 5 * 60

# count number of speeders
n_speeding <- 
  nrow(
    filter(
      d, 
      Duration__in_seconds_ < time_crit
      )
    )

# Deletion of fast respondents
d <- 
  filter(
    d, 
    Duration__in_seconds_ >= time_crit
    )

n_used <- nrow(d)
```

Average response time was `r time_m %>% round(0)` minutes. We removed `r n_speeding` because they answered the survey unreasonably fast.

Let's inspect for potential response patterns.

# Sociodemographics

@@

Let's first inspect age. Here, the age categories were as follows:

1: Under 18 years old
2: 18-24 years old 
3: 25-34 years old 
4: 35-44 years old 
5: 45-54 years old 
6: 55-64 years old 
7: 65+ years old

```{r}
table(d$AGE)
```

@@

```{r}
age_m <- 
  mean(d$AGE)
```

@@

Let's next inspect gender. Categories were:

1: "Man" 
2: "Woman" 
3: "Third gender / Other"

```{r}
table(d$GEN) %>% 
  prop.table() %>% 
  round(2)
```

@@

Let's next inspect education. Categories were:

1: "No college degree" 
2: "College degree"

```{r}
table(d$COL) %>% 
  prop.table() %>% 
  round(2)
```

@@

Let's next inspect ethnicity. Answer categories were as follows:

1: "White"
2: "Other"

```{r}
table(d$ETH) %>%
  prop.table() %>% 
  round(2)
```

@@

# Items

All items were answered on a 7-point scale with the following options:

@@

## Ceiling/Floor effects

@@

```{r}
d %>%
  select(
    paste0(rep(vars_pers_pri, each = 4), "_0", 1:4)
  ) %>% 
  apply(
    2,  mean, na.rm = T
  )
```

No item below floor (1.5) or ceiling (6.5) thresholds.

## Personality
### Honesty Humility
#### Sincerity

 - If I want something from a person I dislike, I will act very nicely toward that person in order to get it.
 - I wouldn't use flattery to get a raise or promotion at work, even if I thought it would succeed.
 - If I want something from someone, I will laugh at that person's worst jokes.
 - I wouldn't pretend to like someone just to get that person to do favors for me.

@@

@@

 - If I knew that I could never get caught, I would be willing to steal a million dollars.
 - I would be tempted to buy stolen property if I were financially tight.
 - I would never accept a bribe, even if it were very large.
 - I’d be tempted to use counterfeit money, if I were sure I could get away with it.

@@

 - Having a lot of money is not especially important to me.
 - I would like to live in a very expensive, high-class neighborhood.
 - I would like to be seen driving around in a very expensive car.
 - I would get a lot of pleasure from owning expensive luxury goods.

@@

 - I am an ordinary person who is no better than others.
 - I wouldn’t want people to treat me as though I were superior to them.
 - I think that I am entitled to more respect than the average person is.
 - I want people to know that I am an important person of high status.

@@

 - I would feel afraid if I had to travel in bad weather conditions.
 - I don’t mind doing jobs that involve dangerous work.
 - When it comes to physical danger, I am very fearful.
 - Even in an emergency I wouldn't feel like panicking.

@@

 - I sometimes can't help worrying about little things.
 - I worry a lot less than most people do.
 - I rarely, if ever, have trouble sleeping due to stress or anxiety.
 - I get very anxious when waiting to hear about an important decision.

@@

 - When I suffer from a painful experience, I need someone to make me feel comfortable.
 - I can handle difficult situations without needing emotional support from anyone else.
 - Whenever I feel worried about something, I want to share my concern with another person.
 - I rarely discuss my problems with other people.

@@

 - I feel like crying when I see other people crying.
 - When someone I know well is unhappy, I can almost feel that person's pain myself.
 - I feel strong emotions when someone close to me is going away for a long time.
 - I remain unemotional even in situations where most people get very sentimental.

@@

 - HEX_EMO with	HEX_EMO_FEA_04

@@

 - I feel reasonably satisfied with myself overall.
 - I think that most people like some aspects of my personality.
 - I feel that I am an unpopular person.
 - I sometimes feel that I am a worthless person.

@@

 - I rarely express my opinions in group meetings.
 - In social situations, I'm usually the one who makes the first move.
 - When I'm in a group of people, I'm often the one who speaks on behalf of the group.
 - I tend to feel quite self-conscious when speaking in front of a group of people.

@@

 - I avoid making "small talk" with people.
 - I enjoy having lots of people around to talk with.
 - I prefer jobs that involve active social interaction to those that involve working alone.
 - The first thing that I always do in a new place is to make friends.

@@

 - I am energetic nearly all the time.
 - On most days, I feel cheerful and optimistic.
 - People often tell me that I should try to cheer up.
 - Most people are more upbeat and dynamic than I generally am.

@@

 - I rarely hold a grudge, even against people who have badly wronged me.
 - My attitude toward people who have treated me badly is "forgive and forget".
 - If someone has cheated me once, I will always feel suspicious of that person.
 - I find it hard to fully forgive someone who has done something mean to me.

@@

 - People sometimes tell me that I am too critical of others.
 - I generally accept people’s faults without complaining about them.
 - I tend to be lenient in judging other people.
 - Even when people make a lot of mistakes, I rarely say anything negative.

@@

 - People sometimes tell me that I'm too stubborn.
 - I am usually quite flexible in my opinions when people disagree with me.
 - When people tell me that I’m wrong, my first reaction is to argue with them.
 - I find it hard to compromise with people when I really think I’m right.

@@

 - People think of me as someone who has a quick temper.
 - I rarely feel anger, even when people treat me quite badly.
 - Most people tend to get angry more quickly than I do.
 - I find it hard to keep my temper when people insult me.

@@

 - I clean my office or home quite frequently.
 - I plan ahead and organize things, to avoid scrambling at the last minute.
 - People often joke with me about the messiness of my room or desk.
 - When working, I sometimes have difficulties due to being disorganized.

@@

 - When working, I often set ambitious goals for myself.
 - I often push myself very hard when trying to achieve a goal.
 - Often when I set a goal, I end up quitting without having reached it.
 - I do only the minimum amount of work needed to get by.

@@

 - I often check my work over repeatedly to find any mistakes.
 - When working on something, I don't pay much attention to small details.
 - I always try to be accurate in my work, even at the expense of time.
 - People often call me a perfectionist.

@@

 - I make decisions based on the feeling of the moment rather than on careful thought.
 - I make a lot of mistakes because I don't think before I act.
 - I don’t allow my impulses to govern my behavior.
 - I prefer to do whatever comes to mind, rather than stick to a plan.

@@

 - I think that paying attention to radical ideas is a waste of time.
 - I like people who have unconventional views.
 - I think of myself as a somewhat eccentric person.
 - I find it boring to discuss philosophy.

>>>>

---
title: "Results"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
---

@@

knitr::opts_chunk$set(
  warning=F
  , echo=T
  , error=F
  , message=F
  , cache=T
  , tidy=T
  # , dev = 'pdf'
  # , cache.extra = knitr::rand_seed
  , fig.height = 4
  , fig.width = 6
  )

@@

# Set-Up

We first load the required packages.

```{r packages, include=T, echo=T, results='hide', cache=F}
# install packages
# devtools::install_github("https://github.com/tdienlin/td")

library(confintr)
library(corrplot)
library(easystats)
library(ggplot2)
library(kableExtra)
library(knitr)
library(lavaan)
library(magrittr)
library(MVN)
library(naniar)
library(PerFit)
library(psych)
library(sjlabelled)
library(semTools)
library(tidyverse)
library(td)
```

We then load the cleaned data.

```{r data, include=T, echo=T, results='hide', cache=T}
load("data/workspace_2.RData")
source("custom_functions.R")
```

# Items Characteristics

In what follows, we report item characteristics.

## Sociodemographics

@@

### Age

```{r}
d$age %>% 
  sjlabelled::as_label() %>% 
  data_tabulate()
```

@@

```{r}
age_m <- 
  mean(d$age)
```

@@

### Gender

```{r}
d$GEN %>% 
  sjlabelled::as_label() %>% 
  data_tabulate()
```

@@

### Education

```{r}
d$COL %>% 
  sjlabelled::as_label() %>% 
  data_tabulate()
```

@@

### Ethnicity

```{r}
d$ETH %>% 
  sjlabelled::as_label() %>% 
  data_tabulate()
```

@@

### Political orientation

```{r}
d$CON %>% 
  sjlabelled::as_label() %>% 
  data_tabulate()
```

We see a certain bias toward participants being liberal as opposed to conservative.

## Personality

All following items were answered on a 7-point scale with the following options:

@@

### Ceiling/Floor effects

@@

```{r}
d_extremes <-
  d %>%
  select(
    paste0(rep(vars_pers_pri, each = 4), "_0", 1:4)
  ) %>% 
  apply(
    2,  mean, na.rm = T
  ) %>% 
  as.data.frame() %>% 
  select(Mean = ".") %>% 
  arrange(Mean)
```

Lowest values:

```{r}
head(d_extremes)
```

No item below floor (1.5) threshold.

Highest values:

```{r}
tail(d_extremes)
```

No item above ceiling (6.5) thresholds.

### Honesty Humility
#### Sincerity

 1. If I want something from a person I dislike, I will act very nicely toward that person in order to get it.
 1. I wouldn't use flattery to get a raise or promotion at work, even if I thought it would succeed.
 1. If I want something from someone, I will laugh at that person's worst jokes.
 1. I wouldn't pretend to like someone just to get that person to do favors for me.

@@

plot_hist(name)
```

```{r}
mardia(
  select(
    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
  )
)
```

@@

 1. If I knew that I could never get caught, I would be willing to steal a million dollars.
 1. I would be tempted to buy stolen property if I were financially tight.
 1. I would never accept a bribe, even if it were very large.
 1. I’d be tempted to use counterfeit money, if I were sure I could get away with it.

@@

 1. Having a lot of money is not especially important to me.
 1. I would like to live in a very expensive, high-class neighborhood.
 1. I would like to be seen driving around in a very expensive car.
 1. I would get a lot of pleasure from owning expensive luxury goods.

@@

 1. I am an ordinary person who is no better than others.
 1. I wouldn’t want people to treat me as though I were superior to them.
 1. I think that I am entitled to more respect than the average person is.
 1. I want people to know that I am an important person of high status.

@@

 1. I would feel afraid if I had to travel in bad weather conditions.
 1. I don’t mind doing jobs that involve dangerous work.
 1. When it comes to physical danger, I am very fearful.
 1. Even in an emergency I wouldn't feel like panicking.

@@

 1. I sometimes can't help worrying about little things.
 1. I worry a lot less than most people do.
 1. I rarely, if ever, have trouble sleeping due to stress or anxiety.
 1. I get very anxious when waiting to hear about an important decision.

@@

 1. When I suffer from a painful experience, I need someone to make me feel comfortable.
 1. I can handle difficult situations without needing emotional support from anyone else.
 1. Whenever I feel worried about something, I want to share my concern with another person.
 1. I rarely discuss my problems with other people.

@@

 1. I feel like crying when I see other people crying.
 1. When someone I know well is unhappy, I can almost feel that person's pain myself.
 1. I feel strong emotions when someone close to me is going away for a long time.
 1. I remain unemotional even in situations where most people get very sentimental.

@@

 1. HEX_EMO with	HEX_EMO_FEA_04

@@

 1. I feel reasonably satisfied with myself overall.
 1. I think that most people like some aspects of my personality.
 1. I feel that I am an unpopular person.
 1. I sometimes feel that I am a worthless person.

@@

 1. I rarely express my opinions in group meetings.
 1. In social situations, I'm usually the one who makes the first move.
 1. When I'm in a group of people, I'm often the one who speaks on behalf of the group.
 1. I tend to feel quite self-conscious when speaking in front of a group of people.

@@

 1. I avoid making "small talk" with people.
 1. I enjoy having lots of people around to talk with.
 1. I prefer jobs that involve active social interaction to those that involve working alone.
 1. The first thing that I always do in a new place is to make friends.

@@

 1. I am energetic nearly all the time.
 1. On most days, I feel cheerful and optimistic.
 1. People often tell me that I should try to cheer up.
 1. Most people are more upbeat and dynamic than I generally am.

@@

 1. I rarely hold a grudge, even against people who have badly wronged me.
 1. My attitude toward people who have treated me badly is "forgive and forget".
 1. If someone has cheated me once, I will always feel suspicious of that person.
 1. I find it hard to fully forgive someone who has done something mean to me.

@@

 1. People sometimes tell me that I am too critical of others.
 1. I generally accept people’s faults without complaining about them.
 1. I tend to be lenient in judging other people.
 1. Even when people make a lot of mistakes, I rarely say anything negative.

@@

 1. People sometimes tell me that I'm too stubborn.
 1. I am usually quite flexible in my opinions when people disagree with me.
 1. When people tell me that I’m wrong, my first reaction is to argue with them.
 1. I find it hard to compromise with people when I really think I’m right.

@@

 1. People think of me as someone who has a quick temper.
 1. I rarely feel anger, even when people treat me quite badly.
 1. Most people tend to get angry more quickly than I do.
 1. I find it hard to keep my temper when people insult me.

@@

 1. I clean my office or home quite frequently.
 1. I plan ahead and organize things, to avoid scrambling at the last minute.
 1. People often joke with me about the messiness of my room or desk.
 1. When working, I sometimes have difficulties due to being disorganized.

@@

 1. When working, I often set ambitious goals for myself.
 1. I often push myself very hard when trying to achieve a goal.
 1. Often when I set a goal, I end up quitting without having reached it.
 1. I do only the minimum amount of work needed to get by.

@@

 1. I often check my work over repeatedly to find any mistakes.
 1. When working on something, I don't pay much attention to small details.
 1. I always try to be accurate in my work, even at the expense of time.
 1. People often call me a perfectionist.

@@

 1. I make decisions based on the feeling of the moment rather than on careful thought.
 1. I make a lot of mistakes because I don't think before I act.
 1. I don’t allow my impulses to govern my behavior.
 1. I prefer to do whatever comes to mind, rather than stick to a plan.

@@

 1. I think that paying attention to radical ideas is a waste of time.
 1. I like people who have unconventional views.
 1. I think of myself as a somewhat eccentric person.
 1. I find it boring to discuss philosophy.
